---
title: "UK Institutional Rights Retention Policies"
subtitle: (CC BY) <https://sje30.github.io/rrs/rrs.html>
date: 2023-03-18
date-format: iso
date-modified: last-modified
author:
  - name: Stephen J. Eglen
    orcid: 0000-0001-8607-8025
    affiliation: University of Cambridge
format:
  html:
    embed-resources: false
---


# Introduction

This page contains information about UK universities that have
institutional rights retention policies.  The raw data underlying
these visualisations is available on
[github](https://github.com/sje30/rrs/blob/main/ukinstitutions.csv)
along with the code that generates this page.  Please also visit a
list of [similar policies worldwide](https://cyber.harvard.edu/hoap/Additional_resources#Policies_of_the_kind_recommended_in_the_guide).


The Open Access Directory has launched a worldwide list of [university
rights-retention OA policies](https://oad.simmons.edu/oadwiki/University_rights-retention_OA_policies).

```{r echo=FALSE, include=FALSE}
library(leaflet)
library(tidyverse)
library(htmltools)
library(DT)
cities = read_csv("places.csv")
rr     = read_csv("ukinstitutions.csv", comment = "#")
merged <- merge(x=rr, y=cities, by="Institution")
merged <- merged %>% mutate(label = sprintf("<a href=\"%s\">%s</a>",
                                            Reference, Institution))
rr <- rr %>% mutate(Policy = sprintf("<a href=\"%s\">link</a>", Reference))
rr <- rr %>% mutate(Reference=NULL)
```

```{r, echo=FALSE, include=TRUE}
leaflet(merged, width=600, height=600) %>% addTiles() %>%
  addMarkers(~long, ~lat, popup = ~label,
            options = popupOptions(closeButton = TRUE))
```

Click on marker and then on Uni name to see their policy.  Some cities
have multiple pins; zoom-in to see them.

## Adding more institutions

If you would like to add new institutions to this page, please
[email](https://sje30.github.io/about) with the name of the
institution, URL and start date.




## In progress

[Rights retention
policies](https://midlandsinnovation.org.uk/write/MediaUploads/Press%20Release/2023/MIRightsRetentionStatementFINAL.pdf)
expected in the Midland consortium of eight universities.

[The Scottish Confederation of University and Research Libraries
(SCURL)](https://www.scurl.ac.uk/rights-retention-statement) will
provide rights retention principles for their institutions.

[The GW4 Alliance](https://gw4.ac.uk/news/gw4-alliance-launches-joint-statement-on-rights-retention-in-scholarly-works/)
(Bath, Bristol, Cardiff and Exeter) has announced in November 2023
their intention for rights retention policies.


## Underlying data

```{r}
datatable(rr,escape=FALSE)
```

